Compare some methods to remove intercept from models
========================================================


These are possible methods to remove the intercept from models fitting bole volume growth to prior bole volume:
* Recenter data around zero
* Fit linear/polynomial/B-spline models and explicitly specify no intercept

Data was centered by subtracting the means.


```{r, echo=FALSE}
library(splines)

## test data
inst <- 1
plt <- 10
tm <- 85

## data: show for install 1 plot 10 time 76
bclong1 <- read.csv("~/work/data/data/long-bc-derived.csv")

## Test data, only look at ALIVE firs that grew
bclong <- subset(bclong1, spec == "FD" & stat == "ALIVE" & bvgrowth>=0) ## not sure how to treat trees
tst <- bclong[bclong$install == inst & bclong$plot == plt & bclong$time == tm,]
```

Test data from install `inst`, plot `plt`, and year `tm`.


```{r fits}
ind <- tst[,"bv"]
dep <- tst[,"bvgrowth"]

## Centered data
indCent <- ind - mean(ind)
depCent <- dep - mean(dep)

## Poly fits
fit1 <- lm(depCent ~ poly(indCent, degree = 3))
fit2 <- lm(depCent ~ poly(indCent, degree = 3) - 1)
fit3 <- lm(dep ~ poly(ind, degree = 3))
fit4 <- lm(dep ~ poly(ind, degree = 3) - 1)

## bs fits
fit5 <- lm(dep ~ bs(ind, degree = 3))
fit6 <- lm(dep ~ bs(ind, degree = 3) - 1)
fit7 <- lm(depCent ~ bs(indCent, degree = 3))
fit8 <- lm(depCent ~ bs(indCent, degree = 3) - 1)

## linear
fit9 <- lm(dep ~ ind)
fit10 <- lm(depCent ~ indCent)
fit11 <- lm(dep ~ ind - 1)
fit12 <- lm(depCent ~ indCent - 1)
```


## Poly
### centered
```{r}
summary(fit1)
summary(fit2)
```

### untransformed
```{r}
summary(fit3)
summary(fit4)
```

## B-spline
### centered
```{r}
summary(fit7)
summary(fit8)
```

### untransformed
```{r}
summary(fit5)
summary(fit6)
```

## Linear
### centered
```{r}
summary(fit10)
summary(fit12)
```

### untransformed
```{r}
summary(fit9)
summary(fit11)
```

